\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in,nofoot]{geometry}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{*1}{*1}

\newcommand{\entry}[4]{
    \noindent\textbf{#1} \hfill #2 \\
    \noindent\textit{#3} \hfill \textit{#4} \\
    \vspace{2pt}
}

\newcommand{\project}[2]{
    \noindent\textbf{#1} \hfill #2 \\
    \vspace{2pt}
}

\begin{document}

\pagenumbering{gobble}

\noindent
\begin{minipage}[t]{0.5\textwidth}
\textbf{\Large RAFAEL ALVES}

\vspace{0.4em}

\noindent \faMapMarker ~ Aracaju, Sergipe, Brazil
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
\raggedleft
{\color{black}} {\faPhone \space +55 (79) 99916-2489} \quad
{\color{blue}} \href{mailto:rafaelalves7393@gmail.com}{\faEnvelope \space rafaelalves7393@gmail.com}

\vspace{0.2em}

{\color{blue}} \href{https://github.com/rafa-alves6}{\faGithub \space GitHub} \quad
{\color{blue}} \href{https://www.linkedin.com/in/rafael-alves-bb0403302/}{\faLinkedin \space LinkedIn} \\
\end{minipage}

\vspace{0.5em}

\section*{Professional Profile}
\vspace{0.4em}
\noindent Systems Development student with a strong foundation in Object-Oriented Design, SOLID principles, and Test-Driven Development, focused on the Java and Spring Boot ecosystem. Experienced in building clean, well-tested RESTful APIs, from data modeling and business logic to securing endpoints. Eager to join a collaborative, feedback-driven team to apply these practices to impactful, real-world software.

\vspace{0.5em}

\section*{Projects}
\vspace{0.6em}
\project{SmartMed API | \normalfont{\textit{Java, Spring Boot, Spring Security, TDD}}}{\textbf{April 2025}}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
    \item Developed a RESTful API to streamline patient management and appointment scheduling for medical clinics.
    \item Applied \textbf{SOLID principles} and \textbf{Object-Oriented Design} to build a clean, maintainable, and scalable architecture.
    \item Wrote unit and integration tests covering transactional operations, following \textbf{ACID fundamentals} and a \textbf{Test-Driven Development (TDD)} approach to ensure code quality and reliability.
    \item Secured API endpoints with Spring Security, applying core application security practices.
\end{itemize}

\project{Banking System API | \normalfont{\textit{Python, Django, REST Framework}}}{\textbf{May 2024}}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
    \item Designed and built a secure RESTful API to handle core banking operations, focusing on data integrity and business logic.
    \item Modeled complex financial transactions and implemented endpoints for a seamless and secure user experience.
    \item Collaborated using Git and GitHub for version control and code reviews.
\end{itemize}


\section*{Experience}
\vspace{0.6em}
\entry{Thoughtworks University -- Batch 95}{\faCalendar \space May 2026 -- May 2027}{Associate Full-Stack Developer (Graduate Program)}{\faMapMarker \space Pune, India / Remote}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
    \item Selected for a 1-year intensive graduate program covering CI/CD, pair programming, and \textbf{Test-Driven Development (TDD)}.
    \item Delivered features for a full-stack event-scheduling application, using \textbf{Java}, \textbf{Spring Boot}, \textbf{React}, and \textbf{TypeScript}, with \textbf{JUnit}, \textbf{Jest}, \textbf{React Testing Library}, and \textbf{Cypress} for test coverage.
    \item Built and maintained \textbf{CI/CD} pipelines with GitHub Actions and containerized services with \textbf{Docker}.
    \item Led, facilitated, and participated in Agile ceremonies (Scrum, XP, Kanban) using Jira and Figma.
    \item Completed introductory sessions on \textbf{Kafka} and \textbf{Kubernetes (K8s)} during the in-person term in Pune, India.
\end{itemize}

\section*{Education}
\vspace{0.6em}
\entry{Federal Institute of Sergipe (IFS)}{\faCalendar \space Feb 2024 -- Present (4th Semester)}{Technologist in Systems Analysis and Development}{\faMapMarker \space Aracaju, Sergipe}

\section*{Certifications}
\vspace{0.6em}

\entry{AWS Certified Cloud Practitioner}{\faCalendar \space Jul 2026 -- Jul 2029}{Amazon Web Services (AWS)}{}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}
    \item Foundational certification covering AWS Cloud concepts, core services, security, architecture, pricing, and support.
\end{itemize}

\section*{Technical Skills}
\vspace{0.6em}
\noindent \textbf{Languages \& Frameworks:} \textbf{Java}, \textbf{Spring Boot}, Spring Framework, \textbf{TypeScript}, \textbf{Kotlin}, JavaScript, React, Python, Django, SQL \\
\noindent \textbf{Principles \& Practices:} \textbf{Object-Oriented Design (OOD)}, \textbf{SOLID}, \textbf{Test-Driven Development (TDD)}, \textbf{CI/CD}, Agile Methodologies, RESTful API Design \\
\noindent \textbf{Testing:} \textbf{JUnit}, \textbf{Cypress}, \textbf{React Testing Library}, Jest \\
\noindent \textbf{Cloud \& DevOps:} \textbf{AWS}, \textbf{Docker}, \textbf{Kubernetes (K8s)}, GitHub Actions \\
\noindent \textbf{Databases \& Tools:} PostgreSQL, SQL Server, Git, GitHub, IntelliJ IDEA, VS Code \\
\noindent \textbf{Languages (Human):} Portuguese (Native), English (Advanced), Spanish (Intermediate)

\section*{Soft Skills}
\vspace{0.6em}
\noindent Collaboration \& Pair Programming, Fast Learner \& Knowledge Sharing, Resilience in Ambiguity, Openness to Feedback, Problem-Solving, Product-Oriented Mindset.

\end{document}
